Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-12 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Run checks on exposure table

```{r echo = FALSE}
exposure_name <- c("Rain_Exposure", "Distance_Exposure")
count <- c(sum(rain_count$count), sum(distance_count$count))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```
```{r}
rain_exposure$county_storm <- transmute(rain_exposure, county_storm = paste0(fips, " ", storm_id))
distance_exposure$county_storm <- transmute(distance_exposure, county_storm = paste0(fips, " ", storm_id))
all_exposure <- full_join(rain_exposure, distance_exposure, by = "county_storm")
both_exposure <- subset(all_exposure, tot_precip >= 75 & storm_dist.x <= 100) #4040 observations
rain_only <- subset(all_exposure, tot_precip >= 75 & storm_dist.x > 100) #4200 obs
distance_only <- subset(all_exposure, tot_precip < 75 & storm_dist.x <= 100) #0 obs
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE)
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100, na.rm = TRUE)
sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE) # It appears that in all county-
                                                                                   # storm pairs, there is ample
                                                                                   # rain to meet criteria        
sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
```

>>>>

```{r echo = FALSE}
exposure_name <- c("Rain_Exposure", "Distance_Exposure")
count <- c(sum(rain_count$count), sum(distance_count$count))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```
```{r}
rain_exposure$county_storm <- transmute(rain_exposure, county_storm = paste0(fips, " ", storm_id))
distance_exposure$county_storm <- transmute(distance_exposure, county_storm = paste0(fips, " ", storm_id))
all_exposure <- full_join(rain_exposure, distance_exposure, by = "county_storm")
both_exposure <- subset(all_exposure, tot_precip >= 75 & storm_dist.x <= 100) #4040 observations
rain_only <- subset(all_exposure, tot_precip >= 75 & storm_dist.x > 100) #4200 obs
distance_only <- subset(all_exposure, tot_precip < 75 & storm_dist.x <= 100) #0 obs
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE)
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100, na.rm = TRUE)
sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE) # It appears that in all county-
                                                                                   # storm pairs, there is ample
                                                                                   # rain to meet criteria        
sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
#Test
rain_exposure_2 <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 100,
                             days_include = c(-1, 0, 1)) # Creates a data frame with 4040 obs (expected)
distance_rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 0, dist_limit = 100,
                             days_include = c(-1, 0, 1)) 
sum(distance_rain_exposure$tot_precip >= 75) # 4040 obs (meet both criteria)
sum(distance_rain_exposure$tot_precip < 75 & distance_rain_exposure$storm_dist <= 100) #7103 obs meet distance but 
                                                                                       #not rain criteria
```
